---
title       : Predicting IRIS species
subtitle    : 
author      : KM Mohsin (mohsin.eee@gmail.com)
job         : Ph.D. candidate, Louisiana State University
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets    : [bootstrap, quiz, shiny, interactive]
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
ext_widgets: {rCharts: [libraries/nvd3]}
---

## Introduction

1. This shiny app is to predict "iris" flower "species" based on "random forest" algorithm. 
2. Once, attributes of flower are given this app will predict the species. 
3. This app also plots k means cluster of "iris" R- dataset.

## Input output
Once input are typed in text box on left panel user should hit "predict" button to see predicted "species". Four attributes are
1.	Sepal Length
2.	Sepal Width
3.	Petal Length
4.	Petal Width

Beside these four numeric input users will be able to choose axis of cluster plot from drop down menu. First drop down menu is for x axis and second one for y axis. Cluster number can be chosen from a numeric input either by typing an integer or just by clicking up/down arrow.

---

## Prediction

"Random forest" machine learning algorithm used to predict speices. 

### Prediction with Random Forest
```{r }
library(randomForest)
data("iris")
mod_rf <- randomForest(Species~.,data=iris,ntrees = 8)
test<-iris[1,1:4]
pred_test<-predict(mod_rf,newdata = test) #results of test
as.character(pred_test)
```

---
## Plot

To explore iris data set we can plot different speices SepalLength vs. SepalWidth to see the different classification. 


```{r echo = F, results = 'asis'}
require(rCharts)
names(iris) = gsub("\\.", "", names(iris))
iris = as.data.frame(iris)

r1<-nPlot(SepalLength ~ SepalWidth,group= 'Species', data = iris, type = 'multiBarChart')
r1$print('chart1')
```


---
## Thanks
### References

1. Shiny app:[https://kmmohsin.shinyapps.io/iris_pred_app_deploy/][1]
2. Git Repo: [https://github.com/MohsinKM/DataProdDev.git] [2]
[1]: https://kmmohsin.shinyapps.io/iris_pred_app_deploy/
 "Title"
[2]: https://github.com/MohsinKM/DataProdDev.git 

